The \ac{RMA} routines described in this section are one-sided communication
mechanisms of the \openshmem{} \ac{API}. While using these mechanisms, the user
is required to provide parameters only on the calling side. A characteristic of
one-sided communication is that it decouples communication from the
synchronization. One-sided communication mechanisms transfer the data but do not
synchronize the sender of the data with the receiver of the data. 

\openshmem{} \ac{RMA} routines are all performed on the symmetric objects.  The
initiator \ac{PE} of the call is designated as \source{}, and the \ac{PE} in
which memory is accessed is designated as \dest{}. In the case of the remote
update routine, \PUT{}, the origin is the \source{} \ac{PE} and the destination
\ac{PE} is the \dest{} PE. In the case of the remote read routine, \GET{}, the
origin is the \dest{} \ac{PE} and the destination is the \source{} \ac{PE}.

Where appropriate compiler support is available, \openshmem{} provides type-generic 
one-sided communication interfaces via \Cstd[11] generic selection
(\Cstd[11]~\S6.5.1.1\footnote{Formally, the \Cstd[11] specification is ISO/IEC 9899:2011(E).})
for block, scalar, and block-strided put and get communication. 
Such type-generic routines are supported for the ``standard \ac{RMA} types''
listed in Table \ref{stdrmatypes}.

The standard \ac{RMA} types include the exact-width integer types defined in
\HEADER{stdint.h} by \Cstd[99]%
\footnote{Formally, the \textit{C99} specification is ISO/IEC~9899:1999(E).}%
~\S7.18.1.1 and \Cstd[11]~\S7.20.1.1. When the \Cstd translation environment
does not provide exact-width integer types with \HEADER{stdint.h}, an
\openshmem implemementation is not required to provide support for these types.

\input{content/stdrmatypes}
